---
title: "second_iteration"
output:
  pdf_document: default
  html_document: default
date: "2024-06-23"
---

```{r}
library(tidyverse)
library(gridExtra) # This is use to create multiple grid when working with ggplot else we would have used par()
```

1. Loading the data
```{r}
college <- read.csv("D:\\R\\ISLR\\College.csv")
View(college)
```

2. Replacing the row names with the name of colleges
3. Calculating acceptance rate by dividing the total accepted students by the total number of studenets who applied.
```{r}
rownames(college) <- college[,1]
college <- college[,-1]
```

4. Converting the variable private to factor
```{r}
college$Private <- as.factor(college$Private)
pairs(college[,1:10])
```

5. Finding Elite universities with Top10perc > 50
```{r}
college$Elite <- college$Top10perc > 50
college$Acceptance_Rate<- round(college$Accept/college$Apps,2)
```

6. Acceptance rate for Private and Non-Private Colleges.
```{r}
college %>% 
  ggplot(aes(x=Private,y=Acceptance_Rate))+
  geom_boxplot()+
  theme_minimal()+
  labs(title="Private or Non Private Coleges vs Acceptance Rate")
```
For Non Private colleges the acceptance rate is slightly higher than non private colleges.

7. What is the situation of graduation rate for private and non private colleges.

```{r}
college %>% 
  ggplot(aes(x=Private,y=Grad.Rate))+
  geom_boxplot(aes(color=Private),show.legend=FALSE)+
  theme_minimal()+
  labs(x="Is Private College ?",
       y="Graduation Rate",
       title="Private or Non-Private Colleges vs Gradutaion Ratio")
```
The Graduation Rate for Private Colleges are higher than the graduation rate for Non-Private Colleges.

8. Graduation Rate for Elite or Non Elite colleges
```{r}
college %>% 
  ggplot(aes(x=Elite,y=Grad.Rate))+
  geom_boxplot(aes(color=Elite),show.legend=FALSE)+
  theme_minimal()+
  labs(x="Is Elite College?",
       y="Graduation Rate",
       title="Elite Colleges vs Graduation Rate")
  
```
Clearly The Elite Colleges have higher Graduation Rate than Non Elite Colleges

8. Is Elite college belog to Private or non Private
```{r}
college %>% 
  ggplot(aes(x=Private))+
  geom_bar(aes(color=Elite,fill=Elite),
           position="fill",
           stat="count",
           width=0.5)+
  theme_minimal()+
  labs(title="The proportion of Elite Colleges within Private and Non-Private Collages")
```

9. Is there a relationship between top 10 high school students admitted and the tution fee

```{r}
college %>% 
  ggplot(aes(x=Outstate,y=Top10perc))+
  geom_point(aes(color=Private,shape=Private))+
  scale_x_log10()+
  geom_smooth()+
  theme_minimal()+
  labs(x="Tution Fees (Log10)",
       title="Relation between Tution Fee and top 10% of High Scholl Admission.")
```
The higher fees correlate to Private Colleges and high number of admission of new students from top 10% of high school class in those colleges as well.

10. Is the Expenditure per student related with the admission of new students from top 10% of high school
```{r}
college %>% 
  ggplot(aes(x=Expend,y=Top10perc))+
  geom_point(aes(color=Private,shape=Private),alpha=0.8)+
  geom_smooth()+
  scale_x_log10()+
  theme_minimal()+
  labs(x="Per Student Expenditure (Log10)",
       y="% of New Students from the Top High School Class",
       title="Relationship between Per Student Expenditure and Elite Admission",
       subtitle="The x axis been scaled with log10")

```
The colleges which have high student expenditure, there seems to be higher admission from top10% of high school classes.

11. Does Student to Faculty Ratio is Related to Graduation Rate

```{r}
college %>% 
  ggplot(aes(x=S.F.Ratio,y=Grad.Rate))+
  geom_point(aes(color=Private))+
  geom_smooth()+
  theme_minimal()+
  labs(x="Student to Faculty Ratio",
       y="Graduation Rate",
       title="Student to Faculty Ratio Vs Graduation Rate")
```
There is Downward Trend Seen. When Student to Faculty Ratio increases The Graduation Rate decreases.
And Student to Faculty Ratio In Private college are lesser than that of Non-Private Colleges.

12. Is the Admission of new Students from top 10% of high school related to the percentage of Phd Faculty present in the university.
```{r}
college %>% 
  ggplot(aes(x=PhD,y=Top10perc))+
  geom_point(aes(color=Private))+
  theme_minimal()+
  labs(x="% of PhD faculty",
       y="% of New Admission from Top High School Class",
       title="Relation Between % of PhD and new admission")
```

